%! Author = Ian's PC
%! Date = 10/25/2023

% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{amsmath}
\usepackage{romannum}

\title{Assignment 4 Writeup}
\author{Ian Chen}
\date{\today}

% Document
\begin{document}
    \maketitle


    \section{Short answer problems}

    \begin{enumerate}
        \item \textit{What is the relation between image classification and object detection?
        Please give two concrete exampleson how they are related (e.g., one is applied to solve another)?}
        % TODO: Answer

        \item \textit{Please compare semantic segmentation, instance segmentation and object detection.
        Describe the similarities and differences.}
        % TODO: Answer

        \item \textit{Describe at least two plausible neural network designs for the task of semantic segmentations.}
        % TODO: Answer

        \item \textit{What are the applications of generative models in solving core computer vision tasks.}
        % TODO: Answer

        \item \textit{Discuss the differences between convolution neural networks and deconvolution neural networks.}
        % TODO: Answer
    \end{enumerate}


    \section{Image Classification}

    \begin{itemize}
        \item \textit{Compare the performance between K-Nearest Neighbor classifier and Adaptive Boosting classifier;}
        % TODO: Answer

        \item \textit{Analyze the performance of these two methods when varying the size of the training set
        and the size of the testing set;}
        % TODO: Answer

        \item \textit{Perform cross-validation to study the hyper-parameters of each method;}
        % TODO: Answer

        \item \textit{Try different feature representations.}
        % TODO: Answer
    \end{itemize}

    \begin{itemize}
        \item \textbf{Comparison.} Please compare the performance of the K-nearest neighbor classifier and the
        Adaboosting classifier. Which classes does K-nearest neighbor do better and which classes does Adaboosting do better, and
        why? How about running time?
        % TODO: Answer

        \item \textbf{Cross-validation.} Perform 5-fold cross-validation for the K-nearest neighbor classifier. Report the
        optimized hyper-parameter K and the corresponding confusion matrix.
        % TODO: Answer

        \item \textbf{Cross-validation \Romannum{2}.} Perform 5-fold cross-validation for the AdaBoosting classifier.
        Report the optimal value for the number of weak classifiers.
        % TODO: Answer
    \end{itemize}
\end{document}